The Country-level Impact of Educational Features on the Rate of Entrepreneurship - Data Gathering and Analysis

### 2014-11-13 GEMDataSource.Rmd
Update GEMDataSource.Rmd

##### Self-esteem will be our key explanatory variable

@@

We are not yet fully sure on how to best control for all these variables though, esspecially as GEM data does not seem to be available in dataset format as such. We may need to build up our own dataset, collecting data from the many national GEM NES reports. We will work on this in the coming weeks.

As for now, as a substitute to all these conditions together, we use GEM indicator called "Perceived Opportunities". For each country, it is the average percentage of individuals who believe there are opportunities to start a business in the area they live in. This is not equivalent to controlling for all the conditions above but it actually tells about all of them from the potential entrepreneur's point of view. Since we look at average individual self-esteem in every OECD country, we believe it is consistent to look at the opportunities perceived by the same potential entrepreneur, that is by the average 18-64-year-old individual of these countries.

>>>>

##### Degree of Self-esteem reinforcement within the education system will be our key explanatory variable

Inglehart showed how personal values are shaped before the age of 20, we will try to show how compulsory education (from 6 to 16 years of age) does shape the individual, especially in terms of self-esteem. Of course, is is not easy to quantify how supportive of students' self-esteem a given education system can be and we are still looking for the most adequate measure.

The closest data we found so far is one of the six items / questions that GEM uses to measure the importance of entrepreneurial education at country-level in its NES Survey. Item D01 states:

In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative.

For now, we use two GEM indicators that relate to self-esteem and confidence. We look at the average "perceived capabilities" of an individual of a given country.

@@

We are not yet fully sure on how best to control for all these variables, especially as GEM NES data does not seem to be available in dataset format as such. We may need to build up our own dataset, collecting data from the many national GEM NES reports. We will work on this in the coming weeks.

As for now, as a substitute to all these conditions together, we use GEM indicator called "Perceived Opportunities". For each country, it is the average percentage of individuals who believe there are opportunities to start a business in the area they live in. This is not equivalent to controlling for all the conditions above but it actually tells about all of them from the potential entrepreneur's point of view. Since we look at average individual self-esteem in every OECD country, we believe it is consistent to look at the opportunities perceived by the average 18-64-year-old individual of these countries.
